Music Perception 1: Analysis

### 2021-06-22 analysis/analysis.Rmd
add exact = FALSE to spearman's tests
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

cor_ioi_dyn_spearman <- cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean, method = "spearman")
cor_ioi_dyn_spearman
```

@@

cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean)
```

@@

cor_kot_for_spearman <- cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean, method = "spearman")
cor_kot_for_spearman
```

@@

cor_kot_pia_spearman <- cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean, method = "spearman")
cor_kot_pia_spearman
```

@@

cor_vel_leg_spearman <- cor.test(vel_all[Subcomponent == "Legato"]$Teaching, vel_all[Subcomponent == "Legato"]$Mean, method = "spearman")
cor_vel_leg_spearman
```

@@

cor_vel_diff_ltos_spearman <- cor.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching, vel_diff_all[Subcomponent == "LtoS"]$Mean, method = "spearman")
cor_vel_diff_ltos_spearman
```

>>>>

cor_ioi_dyn_spearman <- cor.test(ioi[Skill == "dynamics"]$Teaching, ioi[Skill == "dynamics"]$Mean, method = "spearman", exact = FALSE)
cor_ioi_dyn_spearman
```

@@

cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean)

cor.test(ioi_tra[Skill == "dynamics"]$Teaching, ioi_tra[Skill == "dynamics"]$Mean, method = "spearman", exact = FALSE)
```

@@

cor_kot_for_spearman <- cor.test(kot_all[Subcomponent == "Forte"]$Teaching, kot_all[Subcomponent == "Forte"]$Mean, method = "spearman", exact = FALSE)
cor_kot_for_spearman
```

@@

cor_kot_pia_spearman <- cor.test(kot_all[Subcomponent == "Piano"]$Teaching, kot_all[Subcomponent == "Piano"]$Mean, method = "spearman", exact = FALSE)
cor_kot_pia_spearman
```

@@

cor_vel_leg_spearman <- cor.test(vel_all[Subcomponent == "Legato"]$Teaching, vel_all[Subcomponent == "Legato"]$Mean, method = "spearman", exact = FALSE)
cor_vel_leg_spearman
```

@@

cor_vel_diff_ltos_spearman <- cor.test(vel_diff_all[Subcomponent == "LtoS"]$Teaching, vel_diff_all[Subcomponent == "LtoS"]$Mean, method = "spearman", exact = FALSE)
cor_vel_diff_ltos_spearman
```
